Multi sky-view\\ 3D aerosol distribution recovery

### 2013-10-06 article.tex
Last fixes by Yoav and proof reading of the new sections by me.

\usepackage{opex3}
\usepackage{times}
\usepackage{graphicx}
\graphicspath{{./images/}}
\usepackage{epstopdf}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{url}
\usepackage{bm}
\usepackage{enumerate}
\usepackage[]{todonotes} % Add option [disable] to hide all todo notes.
\usepackage{xfrac}
\usepackage{paralist}
\usepackage{cite}
\usepackage{soul}
\usepackage{layouts}
\usepackage{booktabs}
\usepackage{colortbl}

@@

\noindent {\bf Inverse transform sampling}: A tool for RT modeling is
the Monte-Carlo (MC) method. MC considers scattering and extinction as
random phenomena, that are sampled from their probability
distributions.
Inverse transform sampling~\cite{devroye1986sample} is used for
sampling random numbers that comply with a specified
probability density function. Let $u$ be a random number drawn
from a uniform distribution in the interval $[0,1]$. The number $u$
can be transformed into a random variable $X$, whose cumulative
distribution function (CDF) is $F(X)$. The transform is $X =
F^{-1}(u)$.

@@

\noindent{\bf Aerosol}: We used particle-type 6 from the aerosol list
in~\cite{Martonchik2009}. This is a spherical non-absorbing
sea-salt/organic particle, whose anisotropy parameter per color
channel is $[g_{\rm R},g_{\rm G},g_{\rm B}]=[0.763,0.775,0.786]$. Its
corresponding extinction cross sections are $[\sigma^{\rm
  aerosol}_{\rm R}, \sigma^{\rm aerosol}_{\rm G}, \sigma^{\rm
  aerosol}_{\rm
  B}]=[16.5,16.2,15.9]$~\si[sticky-per]{\per\micro\meter\squared}.  At
all channels, $\varpi^{\rm aerosol}=1$. We simulated spatial
distributions using a product of two functions. To express the general
trend of reduced density with altitude $h(k)$ of voxel $k$, we
follow~\cite{Levi1980} and set the first function as
\begin{align}
  f_1[h(k)] = n^{\rm sealevel}
  \exp[-h(k)/H^\mathrm{aerosol}],
\end{align}
where $H^\mathrm{aerosol}=2$~\si{\km}. To express a clustered nature
of aerosol distributions (as clouds), we define blobs in the form of
3D ellipsoids. There may be multiple ellipsoids suspended.  Then
\begin{equation}
  f_2(k) =
  \left\{
    \begin{array}{ll}
      1  & \mbox{ if $k\in$ any blob cluster} \\
      0  & \mbox{ otherwise}
      \label{eq:f2}
    \end{array}
  \right.
  .
  \hspace{-0.05cm}
\end{equation}
The true aerosol distribution is then ${\bm n}^{\rm true}={\cal
  S}\{{\bm f}_1\odot {\bm f}_2\}$, where ${\cal S}$ is 3D spatial
smoothing, obtained by narrow 3D Gaussian filtering. It expresses
non-sharp boundaries of typical distributions. The {\em Haze Blobs}
scene in \cref{fig:distributions}(a) uses two ellipsoids: one is 32km
wide, 2.8km thick and centered at altitude 2.5km; the other is 24km
wide, 2.1km thick and centered at altitude 5km. Horizontal widths
are much larger than the vertical thickness, in consistency with
atmospheric scales. \Cref{fig:simulation-results1} shows
photographs of the {\em Haze Blobs} scene, as simulated by
\cref{eq:bigIA}. \hl{Figs. 6.3 to Fig. 6.14 in every comparison, for display purposes both images underwent same contrast streching operations, and used the same colormap}.

@@

\Cref{fig:scatter_order} shows the contribution by successive
scattering orders. They are derived from the MC image. Photons contributing
to any pixel are accumulated in steps {\tt ii},{\tt v} above.
The contributing photons that stem from just a single scattering event yield \cref{fig:scatter_order}(a). Similarly, contributing photons that had experienced exactly  two or three scattering events yield respectively \cref{fig:scatter_order}(b) and
\cref{fig:scatter_order}(c). First-order scatter yields
most of the energy in the MC image. Radiance by higher order scattering
is mostly evident at the horizon. A horizontal LOS passes through a long and dense part of the atmosphere, while a vertical LOS cuts short through the dense, lower part. Hence,
towards the horizon the probability of high order scattering increases.
\begin{figure}[bt]
  \centering
  \yoavcomment{\includegraphics{images/scatter_order.pdf}}
  \caption{\small Separation of the image shown in \cref{fig:mcgrid}(b) to contributionS
   by successive orders of scattering: (a) first , (b) second, (c) third and (d) forth scattering order.}
  \label{fig:scatter_order}
\end{figure}

@@

\noindent{\bf Forward models and distributions}:
\Cref{fig:results} shows estimation results, corresponding to the
original distributions of \cref{fig:distributions}.
\begin{figure}[t]
  \centering
  \yoavcomment{\includegraphics{images/results}}
  \caption{\small Recoveries of scenes shown in
    \cref{fig:distributions}. Color represents aerosol density, in
    units of $10^{6}~{\rm particles}/{\rm m}^3.$ In (a) and (b)
    images simulated by single-scattering are used as input for the
    recovery.  In (c) and (d), MC simulated images are used as input for the
    recovery.  }
  \label{fig:results}
\end{figure}
Here, the atmosphere domain was defined over a
$20\times20 \times 40$ grid. Cameras were placed
$\sim 7$km apart on a $6\times6$ grid.
In Figs.~\ref{fig:results}(a) and (b), the single-scattering model was
used both in rendering of the raw images, and in the estimation algorithm. In
Figs.~\ref{fig:results}(c) and (d), the MC model (multiple scattering)
rendered the raw images, over which our recovery (Sec.~\ref{sec:inverse-problem}) was tested. Overall, the distributions, the density order of magnitude and
values are consistent.
Errors in Figs.~\ref{fig:results}(a) and (b) stem from random noise, which had
been induced in the raw images. Errors are larger when MC is used to
render the images, since high-order scattering is not accounted for in
\newcolumntype{g}{>{\columncolor{Gray}}r}
\begin{table}[t]
  \centering
  \begin{tabular}{cccccgg}
    \toprule
    Haze   & Forward        & Aerosol                 & Isotropic       & Absorbing & $\delta_{\rm mass}$ & $\epsilon~~$ \\
    scene  & model          & density [$1/{\rm m}^3$] & phase function? & aerosol?  &                     &              \\
     \midrule                                                                                             
    Front  & Single scatter & ${\mathcal{O}}(10^{6})$ &                 &           & 1.1\%               & 18\%         \\
           & Monte Carlo    & ${\mathcal{O}}(10^{6})$ &                 &           & -14\%               & 65\%         \\
    \cmidrule(r){1-5}                                                                                     
     Blobs & Single scatter & ${\mathcal{O}}(10^{6})$ &                 &           & 0\%                 & 14\%         \\
           & Monte Carlo    & ${\mathcal{O}}(10^{6})$ &                 &           & 6.7\%               & 65\%         \\
           & Monte Carlo    & ${\mathcal{O}}(10^{6})$ & $\surd$         &           & -2\%                & 49\%         \\
           & Monte Carlo    & ${\mathcal{O}}(10^{6})$ &                 & $\surd$   & 9.6\%               & 83\%         \\
           & Monte Carlo    & ${\mathcal{O}}(10^{7})$ &                 &           & 23\%                & 98\%         \\
    \bottomrule
  \end{tabular}
  \caption{Relative errors in various simulations. Here ${\mathcal{O}}$ denotes order of magnitude.}
  \label{tbl:mass}
\end{table}
the algorithm of \cref{sec:inverse-problem}. \\

@@

\noindent{\bf Aerosol characteristics}: We used the {\em Haze blobs} scene, but varied the
aerosol characteristics. Compared to the aerosol described in \cref{sec:simul}, we tested two variations. In one variation, the phase function was isotropic, i.e.,
$[g_{\rm R},g_{\rm G},g_{\rm B}]=[0,0,0]$. In the other variation, the aerosol is partly absorbing: its single scattering albedo per color channel is
$[\varpi^{\rm aerosol}_{\rm R},\varpi^{\rm aerosol}_{\rm G},\varpi^{\rm aerosol}_{\rm B}]=
[0.69,0.74,0.78]$.  All rendered images used MC (See Figs.~\ref{fig:simulation_particles}(a)--(c)).
\begin{figure}[b]
  \centering
  \yoavcomment{\includegraphics{images/simulation_particles.pdf}}
  \caption{\small Images simulated by MC, from the same viewpoint, but different
  aerosol characteristics. (a) Haze blobs, characterized in Sec.~\ref{sec:simul}. 
  (b) Partly absorbing aerosol. (c) Aerosol having an isotropic phase function. (d) High aerosol density.}
  \label{fig:simulation_particles}
\end{figure}
Recovery results using $N_{\rm views}=36$ are shown in Figs.~\ref{fig:reconstructions}(a,b)
\begin{figure}[b]
  \centering
  \yoavcomment{\includegraphics{images/reconstructions.pdf}}
  \caption{\small  Recovered distributions when the aerosol is either party absorbing (a),
    has isotropic phase function (b) or has high density (c).}
  \label{fig:reconstructions}
\end{figure}
and in Table~\ref{tbl:mass}. The results indicate that if the aerosol's phase function has smaller anisotropy, recovery of the aerosol's density is easier. We hypothesise that tomography is better served by scattering isotropy, since then significant radiance from any voxel reach cameras in a wide range of directions. This may make back-projection (recovery from cameras to voxels) more accurate. On the other hand, if the phase function is too strongly peaked around one direction, most cameras would not receive much scattered radiance from a voxel, undermining tomography. A very broad research is needed to verify and quantify such dependencies.\\

\noindent{\bf Density scale}: We used the aerosol {\em Haze blobs} distribution
and characteristics as described in Sec.~\ref{sec:simul}, but increased the
aerosol density tenfold everywhere. This significantly increases the effects
of high order scattering, as shown in \cref{fig:cross_sections}(b) and
\cref{fig:simulation_particles}(d). Consequently, $\epsilon$ increases,
when using $N_{\rm views}=36$. Still, \cref{fig:reconstructions}(c) shows
that the spatial distribution outlines are recovered similarly to the other
tests.

@@

We are grateful to David~J. Diner for fruitful discussions and his support at all levels. We thank the reviewers for useful comments. Yoav Schechner is a Landau Fellow - supported by the Taub Foundation. This work is supported by the US-Israel Binational Science Foundation (BSF grant 2012202) and conducted in the Ollendorff Minerva Center. Minerva is funded through the BMBF. Part of this work is performed at the Jet Propulsion
Laboratory, California Institute of Technology, under contract with NASA. 
%The work in Caltech was partly supported by ONR-Global grant  N62909-10-1-4056.

>>>>

\usepackage{opex3}
\usepackage{times}
\usepackage{graphicx}
\graphicspath{{./images/}}
\usepackage{epstopdf}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{url}
\usepackage{bm}
\usepackage{enumerate}
\usepackage[]{todonotes} % Add option [disable] to hide all todo notes.
\usepackage{xfrac}
\usepackage{paralist}
\usepackage{cite}
\usepackage{soul}
\usepackage{layouts}
\usepackage{booktabs}
\usepackage{colortbl}
\usepackage{endnotes}

@@

\noindent {\bf Inverse transform sampling}: A tool for RT modeling is
the Monte-Carlo (MC) method. MC considers scattering and extinction as
random phenomena, that are sampled from their probability
distributions.
Inverse transform sampling~\cite{devroye1986sample} is used for
sampling random numbers that comply with a specified
probability density function. Let $u$ be a random number drawn
from a uniform distribution in the interval $[0,1]$. The number $u$
can be transformed into a random variable $X$, whose cumulative
distribution function (CDF) is $F(X)$. The transform is $X =
F^{-1}(u)$, where $F^{-1}$ denotes the inverse function of $F$.

@@

\noindent{\bf Aerosol}: We used particle-type 6 from the aerosol list
in~\cite{Martonchik2009}. This is a spherical non-absorbing
sea-salt/organic particle, whose anisotropy parameter per color
channel is $[g_{\rm R},g_{\rm G},g_{\rm B}]=[0.763,0.775,0.786]$. Its
corresponding extinction cross sections are $[\sigma^{\rm
  aerosol}_{\rm R}, \sigma^{\rm aerosol}_{\rm G}, \sigma^{\rm
  aerosol}_{\rm
  B}]=[16.5,16.2,15.9]$~\si[sticky-per]{\per\micro\meter\squared}.  At
all channels, $\varpi^{\rm aerosol}=1$. We simulated spatial
distributions using a product of two functions. To express the general
trend of reduced density with altitude $h(k)$ of voxel $k$, we
follow~\cite{Levi1980} and set the first function as
\begin{align}
  f_1[h(k)] = n^{\rm sealevel}
  \exp[-h(k)/H^\mathrm{aerosol}],
\end{align}
where $H^\mathrm{aerosol}=2$~\si{\km}. To express a clustered nature
of aerosol distributions (as clouds), we define blobs in the form of
3D ellipsoids. There may be multiple ellipsoids suspended.  Then
\begin{equation}
  f_2(k) =
  \left\{
    \begin{array}{ll}
      1  & \mbox{ if $k\in$ any blob cluster} \\
      0  & \mbox{ otherwise}
      \label{eq:f2}
    \end{array}
  \right.
  .
  \hspace{-0.05cm}
\end{equation}
The true aerosol distribution is then ${\bm n}^{\rm true}={\cal
  S}\{{\bm f}_1\odot {\bm f}_2\}$, where ${\cal S}$ is 3D spatial
smoothing, obtained by narrow 3D Gaussian filtering. It expresses
non-sharp boundaries of typical distributions. The {\em Haze Blobs}
scene in \cref{fig:distributions}(a) uses two ellipsoids: one is 32km
wide, 2.8km thick and centered at altitude 2.5km; the other is 24km
wide, 2.1km thick and centered at altitude 5km. Horizontal widths
are much larger than the vertical thickness, in consistency with
atmospheric scales. \Cref{fig:simulation-results1} shows
photographs of the {\em Haze Blobs} scene, as simulated by
\cref{eq:bigIA}. \endnote{For clarity of display, the brightness of the
displayed pictures in this paper underwent the same standard
contrast enhancement (stretching), including gamma-correction.
The recovery algorithms, of course, have used the raw (not brightness
enhanced) images.}

@@

\Cref{fig:scatter_order} shows the contribution by successive
scattering orders. They are derived from the MC image. Photons contributing
to any pixel are accumulated in steps {\tt ii} and {\tt v} above.
The contributing photons that stem from just a single scattering event yield
\cref{fig:scatter_order}(a). Similarly, contributing photons that had
experienced exactly  two or three scattering events yield respectively
\cref{fig:scatter_order}(b) and \cref{fig:scatter_order}(c). First-order
scatter yields most of the energy in the MC image. Radiance by higher order scattering
is mostly evident at the horizon. A horizontal LOS passes through a long
and dense part of the atmosphere, while a vertical LOS cuts short through
the dense, lower part. Hence, toward the horizon the probability of high
order scattering increases.
\begin{figure}[bt]
  \centering
  \yoavcomment{\includegraphics{images/scatter_order.pdf}}
  \caption{\small Separation of the image shown in \cref{fig:mcgrid}(b) to contributionS
   by successive orders of scattering: (a) first , (b) second, (c) third and (d) forth scattering order.}
  \label{fig:scatter_order}
\end{figure}

@@

\noindent{\bf Forward models and distributions}:
\Cref{fig:results} shows estimation results, corresponding to the
original distributions of \cref{fig:distributions}.
\begin{figure}[t]
  \centering
  \yoavcomment{\includegraphics{images/results}}
  \caption{\small Recoveries of scenes shown in
    \cref{fig:distributions}. Color represents aerosol density, in
    units of $10^{6}~{\rm particles}/{\rm m}^3.$ In (a) and (b)
    images simulated by single-scattering are used as input for the
    recovery.  In (c) and (d), MC simulated images are used as input for the
    recovery.  }
  \label{fig:results}
\end{figure}
Here, the atmosphere domain was defined over a
$20\times20 \times 40$ grid. Cameras were placed
$\sim 7$km apart on a $6\times6$ grid.
In Figs.~\ref{fig:results}(a) and \ref{fig:results}(b), the single-scattering model was
used both in rendering of the raw images, and in the estimation algorithm. In
Figs.~\ref{fig:results}(c) and \ref{fig:results}(d), the MC model (multiple scattering)
rendered the raw images, over which our recovery (Sec.~\ref{sec:inverse-problem}) was tested.
Overall, the distributions, the density order of magnitude and values are consistent.
Errors in Figs.~\ref{fig:results}(a) and \ref{fig:results}(b) stem from random noise, which had
been induced in the raw images. Errors are larger when MC is used to
render the images, since high-order scattering is not accounted for in
\newcolumntype{g}{>{\columncolor{Gray}}r}
\begin{table}[t]
  \centering
  \begin{tabular}{cccccgg}
    \toprule
    Haze   & Forward        & Aerosol                 & Isotropic       & Absorbing & $\delta_{\rm mass}$ & $\epsilon~~$ \\
    scene  & model          & density [$1/{\rm m}^3$] & phase function? & aerosol?  &                     &              \\
     \midrule                                                                                             
    Front  & Single scatter & ${\mathcal{O}}(10^{6})$ &                 &           & -1.1\%               & 18\%         \\
           & Monte Carlo    & ${\mathcal{O}}(10^{6})$ &                 &           & 14\%               & 65\%         \\
    \cmidrule(r){1-5}                                                                                     
     Blobs & Single scatter & ${\mathcal{O}}(10^{6})$ &                 &           & 0\%                 & 14\%         \\
           & Monte Carlo    & ${\mathcal{O}}(10^{6})$ &                 &           & -6.7\%               & 65\%         \\
           & Monte Carlo    & ${\mathcal{O}}(10^{6})$ & $\surd$         &           & 2\%                & 49\%         \\
           & Monte Carlo    & ${\mathcal{O}}(10^{6})$ &                 & $\surd$   & -9.6\%               & 83\%         \\
           & Monte Carlo    & ${\mathcal{O}}(10^{7})$ &                 &           & -23\%                & 98\%         \\
    \bottomrule
  \end{tabular}
  \caption{Relative errors in various simulations. Here ${\mathcal{O}}$ denotes order of magnitude.}
  \label{tbl:mass}
\end{table}
the algorithm of \cref{sec:inverse-problem}. \\

@@

\noindent{\bf Aerosol characteristics}: We used the {\em Haze blobs} scene, but varied the
aerosol characteristics. Compared to the aerosol described in \cref{sec:simul}, we tested two variations. In one variation, the phase function was isotropic, i.e.,
$[g_{\rm R},g_{\rm G},g_{\rm B}]=[0,0,0]$. In the other variation, the aerosol is partly absorbing: its single scattering albedo per color channel is
$[\varpi^{\rm aerosol}_{\rm R},\varpi^{\rm aerosol}_{\rm G},\varpi^{\rm aerosol}_{\rm B}]=
[0.69,0.74,0.78]$.  All rendered images used MC
(See Figs.~\ref{fig:simulation_particles}(a)--\ref{fig:simulation_particles}(c)).
\begin{figure}[b]
  \centering
  \yoavcomment{\includegraphics{images/simulation_particles.pdf}}
  \caption{\small Images simulated by MC, from the same viewpoint, but different
  aerosol characteristics. (a) Haze blobs, characterized in Sec.~\ref{sec:simul}. 
  (b) Partly absorbing aerosol. (c) Aerosol having an isotropic phase function. (d) High aerosol density.}
  \label{fig:simulation_particles}
\end{figure}
Recovery results using $N_{\rm views}=36$ are shown in Figs.~\ref{fig:reconstructions}(a)
and \ref{fig:reconstructions}(b)
\begin{figure}[b]
  \centering
  \yoavcomment{\includegraphics{images/reconstructions.pdf}}
  \caption{\small  Recovered distributions when the aerosol is either party absorbing (a),
    has isotropic phase function (b) or has high density (c).}
  \label{fig:reconstructions}
\end{figure}
and in \cref{tbl:mass}. The results indicate that if the aerosol's phase function
has smaller anisotropy, recovery of the aerosol's density is easier. We hypothesize that
tomography is better served by scattering isotropy, since then significant radiance from
any voxel reaches cameras in a wide range of directions. This may make back-projection
(recovery from cameras to voxels) more accurate. On the other hand, if the phase function
is too strongly peaked around one direction, most cameras would not receive much scattered
radiance from a voxel, undermining tomography. A very broad research is needed to verify
and quantify such dependencies.\\

\noindent{\bf Density scale}: We used the aerosol {\em Haze blobs} distribution
and characteristics as described in Sec.~\ref{sec:simul}, but increased the
aerosol density tenfold everywhere. This significantly increases the effects
of high order scattering, as shown in \cref{fig:cross_sections}(b) and
\cref{fig:simulation_particles}(d). Consequently, $\epsilon$ increases (\cref{tbl:mass}),
when using $N_{\rm views}=36$. Still, \cref{fig:reconstructions}(c) shows
that the spatial distribution outlines are recovered similarly to the other
tests.

@@

We are grateful to David~J. Diner for fruitful discussions and his support at all
levels. We thank the reviewers for useful comments. Yoav Schechner is a Landau
Fellow - supported by the Taub Foundation. This work is supported by the
US-Israel Binational Science Foundation (BSF grant 2012202) and conducted in the
Ollendorff Minerva Center. Minerva is funded through the BMBF. This work was supported
by NASA's Earth Science Technology Office Advanced Information Systems Technology Program.

\theendnotes
